### 2017-09-29 TF-vldb2018/sec-intro.tex

{Query reformulation (\aka query rewriting /modification) is to generate alternative queries that may produce better answers,
and has been studied for structured queries~\cite{MottinEmpty13}, keyword queries~\cite{YaoQReform12} and graph queries~\cite{MottinGReform15}.
However, different from our study of handling pattern updates, the focus of query reformulation is not on incremental computations.

>>>>

{Query reformulation (\aka query rewriting) is to generate alternative queries that may produce better answers,
and has been studied for structured queries~\cite{MottinEmpty13}, keyword queries~\cite{YaoQReform12} and graph queries~\cite{MottinGReform15}.
However, different from our study of handling pattern updates, the focus of query reformulation is not on incremental computations.
